---
title       : Process Analysis
subtitle    : Shiny App at Work
author      : Mariusz Musiał
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

```{r echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(ggplot2)
library(dplyr)

load("assets/procdata.RData") # load the dataframe

procdata <- procdata %>% filter(Process %in% c("A", "B", "C", "D"))
procdata2 <- procdata[sample(nrow(procdata), size = 20, replace = F),]
```

## Process Analysis App

### It will help you:

> - to get the overview of statistical parameters</li>
> - to transform the data</li>
> - to select time range</li>
> - to view the distribution and scatterplots</li>
> - to test for means equality</li>
> - to test for trend change over time</li>
> * Process Analysis App just does this. It helps to analyze and compare functionally equivalent processes.

--- .class #id &twocol

## Analyze data in two domains

*** =left
Poulation

```{r, echo=FALSE, fig.height=6}
        ga <- ggplot(procdata, aes(x = Process, y = Performance, fill = Process))
        ga <- ga + geom_violin()
        ga <- ga + geom_boxplot(fill = "grey", color = "red", outlier.colour = "red",
                                outlier.size = 3, width = .2)
        ga <- ga + stat_summary(color = "black", fun.y=mean, geom="point", shape=21, size=4)
        ga <- ga + ggtitle("Process Performance")
        ga <- ga + xlab("Process type")
            ga <- ga + ylab("Performance metric")
        ga <- ga + theme(plot.title = element_text(size = rel(2), 
                                                   colour = "darkblue", face = "bold"))
        ga <- ga + theme(axis.title.y = element_text(size = rel(1.5)))
        ga <- ga + theme(axis.title.x = element_text(size = rel(1.5)))
        ga <- ga + theme(axis.text.x = element_text(size = rel(1.5)))
        ga <- ga + theme(axis.text.y = element_text(size = rel(1.5)))
        ga
```

*** =right
Time

```{r, echo=FALSE, fig.height=6}
    g8 <- ggplot(procdata, aes(x = Date, y = Performance, color = Process))
    g8 <- g8 + geom_point(size = 3, alpha = .6)
    g8 <- g8 + geom_smooth(method = "lm", color = "black")
    g8 <- g8 + facet_wrap(~Process)
    g8 <- g8 + ggtitle("Performance trends per Process Type")
    g8 <- g8 + xlab("Process run date")
    g8 <- g8 + ylab("Performance metric")
    g8 <- g8 + theme(legend.position="none")
    g8 <- g8 + theme(axis.text.x = element_text(angle = 90))
    g8 <- g8 + theme(plot.title = element_text(size = rel(2), 
                                               colour = "darkblue", face = "bold"))
    g8 <- g8 + theme(axis.title.y = element_text(size = rel(1.5)))
    g8 <- g8 + theme(axis.title.x = element_text(size = rel(1.5)))
    g8 <- g8 + theme(axis.text.x = element_text(size = rel(1.5)))
    g8 <- g8 + theme(axis.text.y = element_text(size = rel(1.5)))

    g8
```

--- .class #id 

## Review some selected statistics in a tabular form

```{r, echo=FALSE, results='asis'}
# Hint from https://github.com/ramnathv/slidify/issues/414
# 
dynamic_table <- DT::datatable(procdata2[,1:4],
                               options = list(autoWidth = FALSE,
                                              searching = TRUE,
                                              paging = TRUE,
                                              info = FALSE,
                                              pageLength = 5,
                                              ordering = TRUE)
                               )
DT::saveWidget(dynamic_table, 'example.html')
cat('<iframe src="example.html" STYLE="width:100%;height=100%"> </iframe>')
```

The table is live, check it out!

--- .class #id 

## Where to find the stuff?

- [Process Analysis App](https://marioem.shinyapps.io/ProcessAnalysis/)
- [App code on GitHub](https://github.com/marioem/DevelopingDataProducts/tree/master)
- [Presentation code on GitHub]()

*A simple documentation about the app is embedded in the app itself*





